---
title: "Plotting in conquestr"
author: "Dan Cloney"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting in conquestr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

conquestr has two main types of plots.
The first is plots based on the `plot` command in [ACER ConQuest](https://conquestmanual.acer.org/s4-00.html#plot).
These plots are done using the generic function `conquestr::plotRout`
The second is more general plots, usually of the inputs or outputs of IRT estimate.

# Example

## plotRout

```{r plotRout}
library(conquestr)
myRout <- ConQuestRout()
plotRout(myRout)
```

## General Plots

You can plot an arbitrary information function against a distribution of students - a so called information Wright map. 

```{r infoWrightMap}
myDeltaDots <- data.frame(
  id = c(1:10),
  itemid = paste0("item", 1:10),
  delta = rnorm(10)
)

MyTaus <- data.frame(
  id = c(2L, 10L),
  itemId = NA,
  step = c(1L, 1L),
  tau = rnorm(2)
)

myItemList <- makeItemList(deltaDot = myDeltaDots, tau = MyTaus)

myPersons <- rnorm(500, 1, 1)
informationWrightMap(myItems = myItemList, myAbilities = myPersons, minTheta = -6, maxTheta = 6)
```
